Test SUSIE for regions near genes (500kb flanking)

### 2020-06-15 analysis/simulation-susie-ukbchr22.Rmd
susie more genes

>>>>

## Simulation 3
Priors:
```{r para 3}
readLines(paste0(outputdir, "prior-3.R"))
```

SUSIE results:
```{r sim 3 setup}
mrashtag <- "20200527-3"
susietag <- "20200604-3"
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```
```{r sim 3 1, out.width = "98%", out.height="95%"}

name <- "MCM5"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}

name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```
